Generative Adversarial Networks

### 2017-11-27 cs6735/project/draft.tex
continued report

\section{Issues}
There exist several issues that characterize generative adversarial networks. Some are related design of GANs or their underlying network implementations. These issues lay at the forfront of GAN research.

\subsection{Instability}
Generative adversarial networks are often characterized by their instability \citep{2017arXiv170100160G}. The training process makes use of gradient descent which does not guarentee convergence to the Nash equilibrium, the game theory equilibrium that involves two competing players. This is different than network optimization which is common in disciminative models. When each network trains, even if the specified network improves, the other may regress. This sometimes leads to the scenario where each network repeatadly undos the other's progress. This problem is not specific to GANs, but to any game situations \citep{2017arXiv170100160G}. It was shown in the first paper that congergenve was guarenteed if updates could be made to the function space, but no theoretical justification was been found that guarentees convergence within the parameter space \citep{2014arXiv1406.2661G}. However, there is no theoretical proof that that these games should not converge \citep{2017arXiv170100160G}. Typically, adversarial networks often oscilatte between different kinds of samples without converging to an equilibrium.

\subsection{Mode Collapse}
Mode collapse occurs when several different latent space vectors $z$ map to the similiar outputs. For example, the generator may create two images that only differ by colour but were generated with very different latent vectors. Full mode collpase is rare; however, partial mode collapse always occurs and varies by intensity. This occurs ...

$$G^* = min_Gmax_DV(F, D)$$

$$G^* = max_Dmin_GV(F, D)$$

\subsection{Image Quality}
Shape, count, orientation

\subsection{Evaluation}
\subsection{Discrete Data}

\section{Model Variations}
Research within the field of deep generative modeling has increased exponentially since the debut of generative adversarial networks in 2014. Significant improvements are being made with image quality and new applitcations are being found every month.

\begin{figure}
\centering
\includegraphics[scale=0.65]{cumulative_gans}
\caption{The cumulative amount of papers written about generative adversarial networks. The graph shows the exponential growth of GANs within the past three years. Image maintined by Avinash Hindipur \citep{November2017GANZoo}.}
\label{fig:Cumulative Number of GAN papers by Month}
\end{figure}

>>>>

\section{Issues}
There exist several issues that characterize generative adversarial networks. Some are related design of GANs or their underlying network implementations. These issues lay at the forefront of GAN research.

\subsection{Instability}
Generative adversarial networks are often characterized by their instability \citep{2017arXiv170100160G}. The training process makes use of gradient descent which does not guarantee convergence to the Nash equilibrium, the game theory equilibrium that involves two competing players. This is different than network optimization which is common in discriminative models. When each network trains, even if the specified network improves, the other may regress. This sometimes leads to the scenario where each network repeatedly undo's the other's progress. This problem is not specific to GANs, but to any game situations \citep{2017arXiv170100160G}. It was shown in the first paper that convergence was guaranteed if updates could be made to the function space, but no theoretical justification was been found that guarantees convergence within the parameter space \citep{2014arXiv1406.2661G}. However, there is no theoretical proof that that these games should not converge \citep{2017arXiv170100160G}. Typically, adversarial networks often oscillate between different kinds of samples without converging to an equilibrium in a phenomenon called mode collapse.

\subsection{Mode Collapse}
Mode collapse occurs when the generator collapses several different latent space vectors $z$ map to the same outputs. Full mode collapse is rare; however, partial mode collapse always occurs and varies by intensity. For example, the generator may create two images that only differ by colour but were generated with very different latent vectors. This occurs when the capacity of the generator is superior to that of the discriminator. Backpropagation does not necessarily follow the minimax game mentioned earlier and may behave like the maximin version.

$$G^* = max_{D}min_{G}V(F, D)$$

When this occurs, the generator attempts to map every latent vector to the one $x$ variable the discriminator is most likely to guess is real. When training, one can only hope the behavior resembles the minimax version. It is often speculated that the root cause of the issue the particular divergence measure used. Specifically, it is often asserted that mode collapse is caused by the use of Jenson-Shannon divergence; however, the use of Kullback-Leibler divergence has be shown to worsen the problem \citep{2017arXiv170100160G}. As mode collapse is currently an unavoidable reality for GANs, their applications are limited to situations where it is acceptable to generate only a small number of distant samples \citep{2017arXiv170100160G}. A potential solution to this problem is discussed in the following section.

\begin{figure}
\centering
\includegraphics[scale=0.8]{modecollapse}
\caption{An example of mode collapse as demonstrated by Metz \textit{et al.} \citep{2016arXiv161102163M}. The generated samples cluster around only one of the modes and do not spread out as they should. Throughout the training process, this cycle continues does not reach an equilibrium.}
\label{fig:Mode Collapse Example}
\end{figure}

\subsection{Image Quality}
When generating images, problems often arise due to the generators difficulties with perspective, counting and structure \citep{2017arXiv170100160G}. For example, an generated animal may not have a 3D structure, have misplaced limbs or have too many of a specific body part. These issues arise due to the underlying model architecture and are not an inherent problem the adversarial network. Furthermore, generated image resolution has remained relatively low; however, recent improvements outlined in the following section show improvements with regard to resolution \citep{2017arXiv171010196K}.

\subsection{Evaluation}
The evaluation procedure for generative adversarial networks remains an open debate as there exist no clear quantitative measurement to evaluate the models \citep{2017arXiv170100160G}. For example, models with high likelihood may produce poor samples and models with low likelihood may produce realistic samples. Several variations of the GANs examine the tradeoffs of divergence measures other than the original Kullback-Leibler divergence \citep{2015arXiv151101844T}. It can be shown that different metrics favor different models. Therefore, it is important to asses one's model within the context of the whole application \citep{2015arXiv151101844T}.

\subsection{Discrete Data}

\section{Improvements}

\subsection{Mini-Batch Features}

\section{Model Variations}
Research within the field of deep generative modeling has increased exponentially since the debut of generative adversarial networks in 2014. Significant improvements are being made with image quality and new applications are being found every month.

\begin{figure}
\centering
\includegraphics[scale=0.5]{cumulative_gans}
\caption{The cumulative amount of papers written about generative adversarial networks. The graph shows the exponential growth of GANs within the past three years. Image maintined by Avinash Hindipur \citep{November2017GANZoo}.}
\label{fig:Cumulative Number of GAN papers by Month}
\end{figure}
